Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-19 ms.tex
added differential illumination analysis of detector 490

The illumination pattern varies slightly over the course of the AZLab 06 baseline stability test.
The illumination changes are small enough that large amounts of averaging are needed to view it.
We first create a ``flat-field'' image by averaging all illuminated data (images 24 through 1000) during the AZLab 06 baseline test.
We then create an ``average1'' image toward the early parts of the lightcurve (images 24-165) where the flux is lower.
We create an ``average2'' image at late parts of the lightcurve (images 700-1000) where the flux is higher.
Both of the ``average'' and ``average2'' images are divided by the ``flat field'' to reveal subtle changes in illumination.
Finally, a crosscut along the X direction is plotted while averaging 126 pixels in the vertical direction.
The results is that the illumination pattern is not constant in time, with a subtle band centered at X$\approx$ 730 pixels that varies in amplitude.

\begin{figure*}
\gridline{\fig{azlab06_illum_baseline_plot_region.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test}}
\gridline{\fig{azlab06_illum_baselin_differential_profile_plot.pdf}{0.49\textwidth}{Differential fluxes during the early and late parts of the baseline test}}
\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange}
\end{figure*}

>>>>

The illumination pattern varies slightly over the course of the AZLab 06 baseline stability test.
The illumination changes are small enough that large amounts of averaging are needed to view it.
We first create a ``flat-field'' image by averaging all illuminated data (images 24 through 1000) during the AZLab 06 baseline test.
We then create an ``average1'' image toward the early parts of the lightcurve (images 24-165) where the flux is lower.
We create an ``average2'' image at late parts of the lightcurve (images 700-1000) where the flux is higher.
Both of the ``average'' and ``average2'' images are divided by the ``flat field'' to reveal subtle changes in illumination.
Finally, a crosscut along the X direction is plotted while averaging 126 pixels in the vertical direction.
The results is that the illumination pattern is not constant in time, with a subtle band centered near X$\approx$ 730 pixels on Detector 488 that varies in amplitude.

\begin{figure*}
\gridline{\fig{azlab06_illum_baseline_plot_region_488.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
\fig{azlab06_illum_baseline_plot_region_490.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_488.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_490.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange}
\end{figure*}
